Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2013-11-13 paper/paper.tex
added equations in Model and Methods Tested everything on node23.

\documentclass[letterpaper,twocolumn,amsmath,amssymb,pre]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{color}

@@

\section{Model and Methods}
We implement the model of Huang \emph{et al.}  for the behavior of the
MinD and MinE proteins inside the cell~\cite{huang2003dynamic}.  This
model is defined by a set of five reaction-diffusion equations:
\begin{align}
  \frac{\partial n_{?}}{\partial t} &= \text{\davidsays{Actual differential equations here.}}
\end{align}
These equations define the rates of diffusion and reaction shown in
Figure~\ref{fig:reactions}.  \davidsays{Add more text here, describing
  the system and the reactants.  In particular, we want to state that
  MinD:ADP binds ATP (or is hydrolyzed?... check!) to form MinD:ATP,
  which then gets stuck to the cell membrane, which is more likely
  when there is already MinD:ATP bound to the membrane.  The MinE then
  binds to the membrane-bound MinD:ATP.  Finally the whole complex can
  fall off the membrane, at which stage you end up with MinD:ADP and
  are ready to start over.  This is also where we define our
  terminology for the volume and surface densities.}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-601-601-601-1500}
  \caption{Total protein fluctuation of an equilateral triangle with
    larger dimensions (each side is roughly $6\micron$.  The vertical
    axis shows stacked the total number of proteins that are of four
    different compound stages and in the different sections of the
    cell. The time limits have been set to show the broken down
    section of the simulation.}
  \label{box-triangle}

>>>>

\documentclass[letterpaper,twocolumn,amsmath,amssymb,pre]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{color}

@@

\section{Model and Methods}
We implement the model of Huang \emph{et al.}  for the behavior of the
MinD and MinE proteins inside the cell~\cite{huang2003dynamic}.  This
model is defined by a set of five reaction-diffusion equations:

\begin{multline}
  \frac{\partial n_{D:ADP}}{\partial t} = D_D\nabla^2n_{D:ADP}-\sigma_D^{ADP\rightarrow ATP}n_{D:ADP}\\
  +\delta(r-R)\sigma_{de}n_{de}\hspace{3.4cm}
\end{multline}
\begin{multline}
  \frac{\partial n_{D:ATP}}{\partial t} = D_D\nabla^2n_{D:ATP}+\sigma_D^{ADP\rightarrow ATP}n_{D:ADP}\\
  -\sigma(r-R)[\sigma_D+\sigma_{dD}(n_d+n_{de})]n_{D:ATP}
\end{multline}
\begin{multline}
  \frac{\partial n_E}{\partial t} = D_E\nabla^2n_E+\delta(r-R)\sigma_{de}n_{de}\\
  -\delta(r-R)\sigma_E n_d n_E\hspace{3.3cm}
\end{multline}
\begin{multline}
  \frac{\partial n_d}{\partial t} = -\sigma_En_dn_E(R)\\
  +[\sigma_D+\sigma_{dD}(n_d+n_{de})]n_{D:ATP}(R)\hspace{.9cm}
\end{multline}
\begin{multline}
  \frac{\partial n_{de}}{\partial t} = -\sigma_{de}n_{de}+\sigma_En_dn_E(R)\hspace{3cm}
\end{multline}

These equations define the rates of diffusion and reaction shown in
Figure~\ref{fig:reactions}.  \davidsays{Add more text here, describing
  the system and the reactants.  In particular, we want to state that
  MinD:ADP binds ATP (or is hydrolyzed?... check!) to form MinD:ATP,
  which then gets stuck to the cell membrane, which is more likely
  when there is already MinD:ATP bound to the membrane.  The MinE then
  binds to the membrane-bound MinD:ATP.  Finally the whole complex can
  fall off the membrane, at which stage you end up with MinD:ADP and
  are ready to start over.  This is also where we define our
  terminology for the volume and surface densities.}

@@

\begin{figure}
%%  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-600-600-1500}
  \caption{Total protein fluctuation of an equilateral triangle with
    larger dimensions (each side is roughly $6\micron$.  The vertical
    axis shows stacked the total number of proteins that are of four
    different compound stages and in the different sections of the
    cell. The time limits have been set to show the broken down
    section of the simulation.}
  \label{box-triangle}
